Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-07 prop_letter.tex
prop_letter.tex \paragraph{Quantum IVPM and Real-valued Probability Measure} Starting roll-back to d=3...

Notice that $\iota_{\infty}\circ\mu_{0}$ has different core elements
relative to different sub-event spaces so that it has an empty core
relative to all projectors~$\events$. When $d\ge3$, if we have
infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element, i.e., we can always identify a unique state.
However, when we only have finite resources, we usually can only identify
a quantum IVPM to more than one states on different sub-event spaces.
The simplest example add one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, the quantum IVPM
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. A more sophisticating example is the
following.

\begin{example}[Four-dimensional quantum three-interval-valued probability
measure]\label{ex:four-dimensional-three-value}Consider the orthonormal
basis~$\left\{ \ket{00},\ket{01},\ket{10},\ket{11}\right\} $ as
defined in Table~\ref{table:commonBasis}. Let
\begin{eqnarray*}
 &  & \imposs=\bar{\mu}(\mathbb{0})=\bar{\mu}(P_{00})=\bar{\mu}(P_{0\ps})=\bar{\mu}(P_{\ps0})\textrm{ ,}\\
 &  & \necess=\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-P_{00})=\bar{\mu}(\mathbb{1}-P_{0\ps})=\bar{\mu}(\mathbb{1}-P_{\ps0})\textrm{ ,}\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray*}
It is straightforward to verify that $\bar{\mu}$ is a quantum IVPM.

@@

Second, we will prove that $\bar{\mu}$ cannot correspond to any quantum
probability measure by contradiction. Suppose $\mu(P)\in\bar{\mu}(P)$
for some quantum probability measure~$\mu:\events\rightarrow\left[0,1\right]$.
We must have 
\begin{equation}
\mu(P_{00})=\mu(P_{0\ps})=\mu(P_{\ps0})=0\textrm{ .}\label{eq:probability-zero-on-states}
\end{equation}
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=0}^{N-1}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\Tr\left(\rho P\right)=\sum_{j=0}^{N-1}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=0}^{N-1}q_{j}=1$ and $q_{j}>0$. However, no pure
state~$\ket{\phi}$ satisfies $\ip{\phi}{00}=\ip{\phi}{0\ps}=\ip{\phi}{\ps0}=0$
so that we have $\mu(P)\notin\bar{\mu}(P)$ for all quantum probability
measure~$\mu$.\qed\end{example}

>>>>

Notice that $\iota_{\infty}\circ\mu_{0}$ has different core elements
relative to different sub-event spaces so that it has an empty core
relative to all projectors~$\events$. When $d\ge3$, if we have
infinite measurement resource and consider $\bar{\mu}:\events\rightarrow\mathscr{I}_{\infty}$,
by Gleason's theorem, $\mathrm{core}\left(\bar{\mu},\events\right)$
has a unique element, i.e., we can always identify a unique state.
However, when we only have finite resources, we usually can only identify
a quantum IVPM to more than one states on different sub-event spaces.
The simplest example add one extra interval~$\unknown=\left[0,1\right]$
to $\mathscr{I}_{\mathrm{D}}$, and consider $\mathscr{I}_{1}=\left\{ \imposs,\unknown,\necess\right\} $.
Then, the quantum IVPM
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\necess & \text{, if }P=\mathbb{1}\text{ ;}\\
\imposs & \text{, if }P=\mathbb{0}\text{ ;}\\
\unknown & \text{, otherwise.}
\end{cases}\label{eq:homomorphism-1}
\end{equation}
provides no information about any results so that $\mathrm{core}\left(\bar{\mu}_{1},\events'\right)$
contains every density matrix. A more sophisticating example is the
following.\footnote{\yutsung{It seems that our example in 4 dimensions together with
relativity core would be unnecessary complex. Therefore, I roll our
example back to 3 dimensions.}}

\begin{example}[Three-dimensional quantum three-interval-valued probability
measure]\label{ex:three-dimensional-three-value} Given a three dimensional
Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Let $\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $, $\ket{\ps}=\left(\ket{0}+\ket{1}\right)/\sqrt{2}$,
$\ket{\ps'}=\left(\ket{0}+\ket{2}\right)/\sqrt{2}$, and
\begin{eqnarray}
 &  & \begin{split}\imposs & =\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})\\
 & =\bar{\mu}(\proj{\ps})=\bar{\mu}(\proj{\ps'})\textrm{ ,}
\end{split}
\\
 &  & \begin{split}\necess & =\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}-\proj{0})\\
 & =\bar{\mu}(\mathbb{1}-\proj{\ps})=\bar{\mu}(\mathbb{1}-\proj{\ps'})\textrm{ ,}
\end{split}
\\
 &  & \unknown=\bar{\mu}(P)\qquad\textrm{otherwise.}
\end{eqnarray}
It is straightforward to verify that $\bar{\mu}$ is a quantum interval-valued
probability measure.

@@

Now assume there exists a real-valued quantum probability measure
$\mu$ such that $\mu(P)\in\bar{\mu}(P)$ for every event (projection)~$P$.
We derive a contradiction as follows. Suppose $\mu(P)\in\bar{\mu}(P)$
then we must have $\mu(\proj{0})=\mu(\proj{\ps})=\mu(\proj{\ps'})=0$.
By Gleason's theorem, there is a mixed state~$\rho=\sum_{j=1}^{N}q_{j}\proj{\phi_{j}}$
such that $\mu\left(P\right)=\sum_{j=1}^{N}q_{j}\ip{\phi_{j}}{P\phi_{j}}$,
where $\sum_{j=1}^{N}q_{j}=1$ and $q_{j}>0$. However, no pure state~$\ket{\phi}$
can satisfy $\ip{\phi}{0}=\ip{\phi}{\ps}=\ip{\phi}{\ps'}=0$; a contradiction.
\end{example}
